sentiment-analysis

### 2016-08-04 eda/sentiment-analysis.Rmd

# calculate mean for each group of stars
# Tidied csv: review_id, star rating, average sentiment score
review_scores <- reviews_text %>% 
  inner_join(valence_score, by = "word") %>% 
  group_by(review_id, stars) %>% 
  summarise(sentiment = mean(score))
```

@@

Positive correlation exists! Some inaccuracy (outliers on boxplots). Find out most common positive and negative words in reviews, creating a summary of the counts.
```{r}
# create summary of words and their average sentiment score in each unique
# review and filter for >= 500 reviews and >= 10 businesses
# Tidied csv: word, # of businesses word appears, # of reviews word appears,
# # of different uses of word, average stars of word
review_words <- reviews_text %>% 
  count(review_id, business_id, stars, word) %>% 
  ungroup()
summaries <- review_words %>% 
  group_by(word) %>% 
  summarise(business = n_distinct(business_id),
            reviews = n(),
            use = sum(n),
            average_star = mean(stars)) %>% 
  ungroup() %>% 
  filter(reviews >= 500, business >= 10) %>% 
  inner_join(valence_score, by = "word")
head(summaries, n = 10)
```

```{r fig.height = 7, fig.width = 7}
summaries %>% 
  ggplot(aes(reviews, average_star, color = score)) +
  geom_point() +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1, hjust = 1) +
  scale_x_log10(limits = c(200, 100000), 
                breaks = c(1000, 10000), labels = c(1000, 10000)) +
  geom_hline(yintercept = mean(reviews$stars), color = "black", lty = 2) +
  scale_color_gradient2(low = "red", high = "blue", midpoint = 0, mid = "gray") +
  labs(x = "# of reviews",
       y = "Average Stars",
       color = "AFINN") +
  theme_bw()
```

>>>>

# calculate mean for each group of stars
review_scores <- reviews_text %>% 
  inner_join(valence_score, by = "word") %>% 
  group_by(review_id, stars) %>% 
  summarise(sentiment = mean(score))
```

@@

Positive correlation exists! Some inaccuracy (outliers on boxplots). Find out most common positive and negative words in reviews, creating a summary of the counts.

```{r fig.width = 8}
review_words <- reviews_text %>% 
  count(review_id, business_id, stars, word) %>% 
  ungroup()
summaries <- review_words %>% 
  group_by(word) %>% 
  summarise(business = n_distinct(business_id),
           reviews = n(),
           use = sum(n),
           average_star = mean(stars)) %>% 
  ungroup() %>% 
  filter(reviews >= 500, business >= 10) %>% 
  inner_join(valence_score, by = "word")

summaries %>% 
  ggplot(aes(reviews, average_star, color = score)) +
  geom_point() +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1, hjust = 1) +
  scale_x_log10(limits = c(0, 200000)) +
  geom_hline(yintercept = mean(reviews$stars), color = "black", lty = 2) +
  scale_color_gradient2(low = "red", high = "blue", midpoint = 0, mid = "gray") +
  labs(x = "# of reviews",
       y = "Average Stars",
       color = "AFINN") +
  theme_bw()
```
